The Impact of Educational Expenses of New Coders

### 2021-04-22 outputs/paper/paper.Rmd
Add multicollinearity diagnostics table

```{r}
#### Beta ####
# TODO: create a bar plot to show which variable affects the most 
QuantPsyc::lm.beta(multiReg2)
QuantPsyc::lm.beta(multiReg3)
```

```{r}
#### Check multicollinearity with Variance Inflation Factor (VIF) & Tolerance ####

### VIF
car::vif(multiReg2)
car::vif(multiReg3)

### Tolerance
1/car::vif(multiReg2)
1/car::vif(multiReg3)
```

# Results

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Multicollinearity diagnostics ####
# Check multicollinearity with Variance Inflation Factor (VIF) & Tolerance

multicolDiagno <- function(mode, title) {
  betaModel2 <- QuantPsyc::lm.beta(mode)
  vifModel2 <- car::vif(mode)
  tolModel2 <- 1/car::vif(mode)

  dfMulticol <-
    betaModel2 %>%
    rbind(formatNumber(unname(betaModel2), 3)) %>%
    rbind(formatNumber(unname(vifModel2), 3)) %>%
    rbind(formatNumber(unname(unname(tolModel2)), 3)) %>%
    cbind(c("B", "Beta", "VIF", "Tolerance"))
    # dplyr::relocate(Metric, .before = CityPopulation) %>%
    # dplyr::select(Metric, everything()) %>%
    # kable()

  ### Relocate 'Metric' column: alternative to 'dplyr::relocate()'
  dfMulticol <- dfMulticol[-1,]
  dfMulticol <- dfMulticol[,c(ncol(dfMulticol),1:ncol(dfMulticol)-1)]

  kable(dfMulticol, 
        caption = title,
        booktabs = TRUE)
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Multicollinearity diagnostics for Model (2) ####
multicolDiagno(multiReg2, "Results of multicollinearity diagnostic metrics for Model (2)")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Multicollinearity diagnostics for Model (3) ####
multicolDiagno(multiReg3, "Results of multicollinearity diagnostic metrics for Model (3)")
```

# Results
```{r, include=FALSE}
#### Beta ####
# TODO: create a bar plot to show which variable affects the most with Beta
```
